SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net

### 2021-04-04 My-Papers/SpecHunter/overview.tex
checkpoint

So, we are ready to turn chopped graphs into small, yet full-blown Bayesian
networks.

\subsection{Graph Splitting}

@@

% TODO: self_question_n_answer.py가 interaction 한번에 얼마나 걸리는지를 측정해
% 그래프로 그리기
After we are done making the initial graph, we chop it down to small graphs of
size under a certain threshold, which will later be converted into Bayesian
networks. This breaking down is necessary since the time consumed during loopy
belief propagation and D-separation algorithms, which will be discussed later
in the next section, gets increasingly inefficient as the graph size increases. Since we are aiming
to reduce the time for a single interaction under \emph{xx??} seconds, we
decided that the optimal threshold for a graph is \emph{180??}. The algorithm
for this task is described in figure \emph{??}. This algorithm relies heavily on
the Kernighan-Lin partitioning algorithm, % TODO: should we cite the algorithm's paper?
which partitions the given graph $G=(V, E)$ into two graphs $G_1=(V_1,E_1)$ and
$G_2=(V_2, E_2)$, such that $V_1$ and $V_2$ are almost equal and the edges
connecting $G_1$ and $G_2$ are minimized. % TODO: read the Kernighan-Lin paper!
% is it really 'minimized'??

\paragraph{Decycling, and controlling in-edges}

Since Bayesian networks are DAGs, we need to eliminate all cycles before we turn
the splitted graphs into Bayesian networks.

@@

>>>>

Since a CPT has a constraint that the sum of probabilities assigned to each cell
of a column is 1, we can come up with the following formula to calculate a
concrete probability value for a cell's relative magnitude of probability.
Suppose we call four cells of a column $cell_1$, $cell_2$, $cell_3$, $cell_4$,
then the probability value of one of the four cells is:

\begin{equation*}
  prob(cell) = \frac{mag(cell)\times coeff(mag(cell))}{\sum_{i=1}^{4}mag(cell)\times coeff(mag(cell_i))}
\end{equation*}

where $mag$ is the score based on relative magnitude: we give $1$ to cells whose
probability should be ``very low'', and $4$ to cells whose probability should be
``very high''. $coeff$ of a relative magnitude is a constant that is multiplied
to the magnitude score. It helps to widen the gap between probabilities assigned
to cells in a column, bearing different relative magnitudes.

\subsection{Graph Manipulation}

% TODO cite networkx 
Here, we explain how we cut the big graph into a handful of small ones, and
further preprocess them before turning each into a Bayesian network. We used
\emph{networkx}'s implementation for each core algorithms: Kernighan-Lin
bisection and cycle detection.

@@

% TODO: self_question_n_answer.py가 interaction 한번에 얼마나 걸리는지를 측정해
% 그래프로 그리기
After we are done making the initial graph, we chop it down to small graphs of
size under a certain threshold, which will later be converted into Bayesian
networks. This breaking down is necessary since the time consumed during loopy
belief propagation and D-separation algorithms, which will be discussed later
in the next section, gets increasingly inefficient as the graph size increases. Since we are aiming
to reduce the time for a single interaction under \emph{xx??} seconds, we
decided that the optimal threshold for a graph is \emph{180??}. The algorithm
for this task is described in figure \emph{??}. This algorithm relies heavily on
the Kernighan-Lin partitioning algorithm, % TODO: should we cite the algorithm's paper?
which partitions the given graph $G=(V, E)$ into two graphs $G_1=(V_1,E_1)$ and
$G_2=(V_2, E_2)$, such that $V_1$ and $V_2$ are almost equal and the edges
connecting $G_1$ and $G_2$ are minimized. % TODO: at least skim the Kernighan-Lin paper!
% is it really 'minimized'??

\paragraph{Decycling, and Controlling in-edges}

Since Bayesian networks are directed acyclic graphs (DAGs), we need to eliminate
all cycles before we turn the splitted graphs into Bayesian networks. We first
use \emph{networkx}'s cycle
detection algorithm which pinpoints the set of edges forming a cycle by
searching the graph in a depth-manner for this task. We then randomly pick one of
such edges causing a cycle and delete it. Repeatedly applying the two
operations until the algorithm fails to detect a cycle, we transform the
splitted graphs into DAGs.      % TODO 이거 figure로 굳이 뺄 필요 없겠지...?

% 'incoming edge가 너무 많아서도, 너무 적어서도 안 된다.'
Next, we control the number of incoming edges of each node. It is already
mentioned that the size of a node's CPT is exponential to the number of its
parent nodes. To our empirical knowledge, if the number of incoming edges (hence
the number of parent nodes) becomes more than 6, the process of converting the
graph into a Bayesian network becomes drastically intractable. Therefore, we
use a simple algorithm to deal with those.

After all these processing, we are finally ready to turn chopped graphs into
small, yet full-blown Bayesian networks.

@@

Here, we expound on the core inference algorithm.
